---
title: "PGM in NLP"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Maximum Entropy Classifier

### No assumption of feature independence ??

### What if most feature functions are of paticular class ?? (feature functions imbalance)
$Accuracy
[1] 0.624031

$per.class
      Precision    Recall F-measure Accuracy FPR TPR AUC
FALSE 0.6921329 0.6988816 0.6954909       NA  NA  NA  NA
TRUE  0.5127610 0.5047967 0.5087477       NA  NA  NA  NA
